RNA-seq from 4 cell populations

### 2022-03-30 deconvolution/fans4/molec_profiling.Rmd
update paths

# file= '/sc/arion/projects/CommonMind/data/resources/GTEx/GTEx_Tissue_colors.csv'
file = synGet('syn22321106')$path
gtexColors = read.csv( file, header=TRUE)
```

>>>>

file= '/sc/arion/projects/CommonMind/data/resources/GTEx/GTEx_Tissue_colors.tsv'
# file = synGet('syn22321106')$path
gtexColors = read.table( file, header=TRUE, sep="\t")
```
